CLT item selection

### 2022-05-06 analysis/clt_data_processing.Rmd
add group comparison DIF

ggplot(dist, aes(x = reorder(targetWord,aoa_german_comb), y = n, fill = chosenCategory))+
  geom_bar(stat ="identity")+
  scale_fill_colorblind(name = "Distractor type", labels = c("Semantic","Phonological","Unrelated"))+
  theme_minimal()+
  labs(x = "Target word", y = "Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
                legend.direction = "vertical",
        legend.position = c(0.1,0.8), 
        legend.spacing.y = unit(0, 'cm'))
```
# Reliability

@@

>>>>

ggplot(dist, aes(x = reorder(targetWord,aoa_german_comb), y = n, fill = chosenCategory))+
  geom_bar(stat ="identity")+
  scale_fill_colorblind(name = "Distractor type", labels = c("Semantic","Phonological","Unrelated"))+
  theme_minimal()+
  labs(x = "Target word", y = "Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
                legend.direction = "vertical",
        legend.position = c(0.1,0.8), 
        legend.spacing.y = unit(0, 'cm'))
```

# Reliability

@@

# Group differneces

```{r}
data%>%
  group_by(sex)%>%
  summarise(mage = mean(age))

sex_dif <- data%>%
  group_by(sex)%>%
  tidyboot_mean(col = correct)

ggplot(sex_dif, aes(x = sex, y = mean))+
  geom_bar(stat = "identity", alpha = .25)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  theme_minimal()
```

```{r}
data%>%
  group_by(order)%>%
  summarise(mage = mean(age))

order_dif <- data%>%
  group_by(order)%>%
  tidyboot_mean(col = correct)

ggplot(order_dif, aes(x = order, y = mean))+
  geom_bar(stat = "identity", alpha = .25)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  theme_minimal()
```

### 2022-05-06 analysis/clt_item_selection.Rmd
add group comparison DIF

# Optimum subset selection via simulated annealing

@@

## Split by Order

params_order_p <- params_order%>%
  group_by(nlpar)%>%
  mutate(sd = sd(order_dif), 
         cut_low = mean(order_dif)-2*sd,
         cut_high = mean(order_dif)+2*sd)

ggplot(params_order_p, aes(x = order_dif))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_histogram(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

exclude_order <- params_order_p%>%
  filter(order_dif < cut_low | order_dif > cut_high)%>%
  pull(item)

model_params <- all_model_params%>%
  filter(!item %in% exclude_sex,
         !item %in% exclude_order)
```

@@

@@

  sim_size <- bind_rows(sim_size, cor)
}

@@

sim_size%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

@@

   sim <- simulated_annealing(20)

@@

icc3 %>% 
  filter(item %in% frq_sel_items)%>%
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line() +
  geom_textline(aes(label = item)) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  #guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  labs(title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
## Correaltion selected with full test

@@

ggplot(compsel, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()
```

>>>>

# Differential item functioning

@@

## Split by Order
### not necessary since model comparison says order adds no predictive value

# params_order_p <- params_order%>%
#   group_by(nlpar)%>%
#   mutate(sd = sd(order_dif), 
#          cut_low = mean(order_dif)-2*sd,
#          cut_high = mean(order_dif)+2*sd)
# 
# ggplot(params_order_p, aes(x = order_dif))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_histogram(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# 
# ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_point(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# exclude_order <- params_order_p%>%
#   filter(order_dif < cut_low | order_dif > cut_high)%>%
#   pull(item)
# 
# 
# model_params <- all_model_params%>%
#   filter(!item %in% exclude_sex,
#          !item %in% exclude_order)
```

@@

for (j in 1:6) {

	sub_dat <- data%>%
	  filter(targetWord %in% sel)%>%
	  group_by(subjID)%>%
	  summarise(mean_sub = mean(correct))

	cor <- cor(sub_dat$mean_sub,full$mean_full)

	row <- tibble(size = i, 
         iter = j, 
         cor = cor)

  sim_size <- bind_rows(sim_size, row)
}

sim_size%>%
  ggplot(aes(x = factor(size), y = cor))+
  geom_point(pch = 1)+
  geom_line(aes(group = factor(iter), lty = factor(iter)))+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

```{r, warning=FALSE}
sim_size_age <- tibble()

@@

  sim_size_age <- bind_rows(sim_size_age, cor)
}

@@

sim_size_age%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

@@

   sim <- simulated_annealing(15)

@@

icc3 %>% 
  filter(item %in% frq_sel_items)%>%
  #filter(item == "orchid")%>%
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line() +
  geom_line(col = "firebrick", alpha = .5) +
  #geom_textline(aes(label = item)) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  labs(#title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
## Correaltion selected with full test

@@

ggplot(compsel, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  #facet_wrap(~age_group)+
  labs(#title = "ICCs for selected items",
       x = "Full test - proportion correct",
       y = "Short test - proportion correct") +
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()
```
